\section{Climate}

\subsection{Current Climate}

\subsection{Projected Climate}

\subsection{Effects of Climate Change}

\subsection{Rating Guide}
Considering these climate-related factors allows for a
comprehensive evaluation of a country's climate conditions,
its response to climate change challenges, and its
commitment to environmental sustainability on both national
and global levels.
\begin{enumerate}
  \item \textbf{Temperature Range}: The typical range of
  temperatures throughout the year, including seasonal
  variations and extreme temperature conditions.
  
  \item \textbf{Precipitation Patterns}: The distribution of
  rainfall and snowfall across different seasons, impacting
  water resources, agriculture, and ecosystems.
  
  \item \textbf{Climate Zones}: The presence of various climate
  zones within the country, such as tropical, arid, temperate,
  and polar climates, influencing biodiversity and agricultural
  suitability.
  
  \item \textbf{Extreme Weather Events}: The frequency and intensity
  of extreme weather events, such as hurricanes, droughts, floods,
  and wildfires, affecting infrastructure resilience and disaster
  preparedness.
  
  \item \textbf{Sea Level Rise}: The vulnerability of coastal areas
  to sea level rise and its potential impact on communities,
  infrastructure, and natural habitats.
  
  \item \textbf{Climate Change Adaptation}: The country's efforts
  and policies to adapt to the impacts of climate change, including
  strategies for water management, agriculture, and urban planning.
  
  \item \textbf{Greenhouse Gas Emissions}: The country's contribution
  to greenhouse gas emissions, which play a role in global climate
  change and environmental sustainability.
  
  \item \textbf{Renewable Energy Adoption}: The extent to which the
  country promotes and utilizes renewable energy sources as part of
  its climate change mitigation efforts.
  
  \item \textbf{Air Quality}: The level of air pollution and its
  impact on public health and environmental well-being.
  
  \item \textbf{Natural Resources}: The management of natural
  resources, such as forests and water bodies, for conservation
  and sustainable use in the context of climate change.
  
  \item \textbf{Climate Policies and Agreements}: The country's
  commitment to international climate agreements and the
  implementation of national climate policies to reduce carbon
  emissions.
  
  \item \textbf{Public Awareness and Engagement}: The level of
  public awareness and engagement in climate-related issues and
  sustainable practices.
  
  \item \textbf{Climate Resilience and Vulnerability}: The country's
  capacity to withstand and recover from climate-related shocks and
  its vulnerability to climate impacts.
\end{enumerate}


