\section{Health Care}

\subsection{Access}

\subsection{Cost}

\subsection{Quality}

\subsection{Rating Guide}
Considering these healthcare-related factors allows for a
comprehensive evaluation of a country's healthcare system,
reflecting its commitment to promoting health, providing
adequate medical care, and improving the overall well-being
of its population.
\begin{enumerate}
  \item \textbf{Healthcare Access}: The availability and
  accessibility of healthcare services, including the
  density of healthcare facilities and the geographical
  distribution of services.
  
  \item \textbf{Healthcare Quality}: The standard of
  healthcare services provided, encompassing the
  qualifications and competence of healthcare professionals,
  as well as adherence to best practices and safety protocols.
  
  \item \textbf{Healthcare Affordability}: The cost of
  healthcare services and the extent of financial
  protection or health insurance coverage for citizens,
  ensuring that healthcare is accessible to all.
  
  \item \textbf{Healthcare Infrastructure}: The capacity
  and readiness of the healthcare system to respond to
  public health emergencies, epidemics, and pandemics.
  
  \item \textbf{Mental Health Services}: The availability
  and accessibility of mental health services and support
  for mental health disorders.
  
  \item \textbf{Healthcare Workforce}: The size and competency
  of the healthcare workforce, including doctors, nurses, and
  other medical professionals.
  
  \item \textbf{Emergency Medical Services}: The efficiency
  and responsiveness of emergency medical services, including
  ambulance availability and response times.
\end{enumerate}
