\section{Path to Citizenship}

\subsection{Rating Guide}
Considering these factors allows for a comprehensive
evaluation of a country's approach to citizenship,
reflecting its commitment to inclusivity, integration,
and the rights of immigrants and long-term residents.
\begin{enumerate}
  \item \textbf{Citizenship Requirements}: The criteria
  and conditions for obtaining citizenship, including
  residency period, language proficiency, and financial
  obligations.
  
  \item \textbf{Naturalization Process}: The efficiency
  and transparency of the naturalization process, including
  application processing time and administrative procedures.
  
  \item \textbf{Dual Citizenship}: The country's stance on
  dual citizenship, which can affect individuals' rights and
  obligations in both their home and adopted countries.
  
  \item \textbf{Citizenship by Birth or Descent}: The provisions
  for acquiring citizenship based on birth within the country's
  territory or through descent from citizens.
  
  \item \textbf{Citizenship for Long-Term Residents}: The
  availability of a pathway to citizenship for long-term
  residents and legal immigrants, promoting integration
  and social cohesion.
  
  \item \textbf{Language and Cultural Integration}: The
  emphasis on language and cultural integration programs
  to facilitate the integration of newcomers into society.
  
  \item \textbf{Citizenship Test and Interview}: The nature
  and significance of citizenship tests and interviews,
  assessing applicants' knowledge of the country's history,
  culture, and institutions.
  
  \item \textbf{Revocation of Citizenship}: The conditions and
  procedures for the revocation of citizenship, including measures
  to prevent statelessness.
  
  \item \textbf{Public Perception and Social Acceptance}: The level
  of public acceptance and support for granting citizenship to
  immigrants, influencing societal cohesion and inclusivity.
  
  \item \textbf{Political Climate}: The political environment and
  its impact on immigration policies and attitudes toward granting
  citizenship.
  
  \item \textbf{Citizenship Benefits and Rights}: The rights and
  privileges associated with citizenship, such as voting rights,
  access to social services, and employment opportunities.
  
  \item \textbf{Integration Support Services}: The availability of
  support services, such as orientation programs and language
  classes, to assist newcomers in their path to citizenship.
\end{enumerate}
