\section{Social State of the Country}

\subsection{Democratic Status}

\subsection{Culture}

\subsection{Humanist Values}
Homophobia, racism, etc...

\subsection{Immigration Policy}

\subsection{Social Trajectory}

\subsection{Rating Guide}
When rating a country on social status, several key factors
should be considered to provide a comprehensive assessment.
Considering these aspects allows for a comprehensive evaluation
of a country's social status, taking into account the well-being
and quality of life of its citizens. A higher social status rating
indicates a society that prioritizes inclusivity, equality, and the
overall welfare of its people:
\begin{enumerate} 
  \item \textbf{Income Equality}: The distribution of wealth and
  income among the population, aiming for a more equitable society.
  
  \item \textbf{Employment Opportunities}: The availability of
  job opportunities, the unemployment rate, and job security
  for citizens.
  
  \item \textbf{Social Safety Nets}: The presence and effectiveness
  of social welfare programs to support vulnerable populations and
  provide a safety net for those in need.
  
  \item \textbf{Gender Equality}: The level of gender equality in
  areas such as education, employment, and representation in
  decision-making roles.
  
  \item \textbf{Racial and Ethnic Harmony}: The existence of a
  harmonious society that respects and celebrates diversity and
  ensures equal treatment for all racial and ethnic groups.
  
  \item \textbf{Access to Basic Needs}: The extent to which citizens
  have access to food, clean water, housing, and other basic
  necessities of life.
  
  \item \textbf{Crime Rates and Public Safety}: The prevalence of
  crime and the effectiveness of law enforcement in maintaining
  public safety.
  
  \item \textbf{Social Cohesion}: The degree of social unity and
  trust among citizens, fostering a sense of community and cooperation.
  
  \item \textbf{Human Rights and Civil Liberties}: The protection and
  promotion of human rights and civil liberties, ensuring individual
  freedoms are upheld.
  
  \item \textbf{Cultural and Recreational Opportunities}: The
  availability of cultural and recreational activities that
  enhance the quality of life for citizens.
  
  \item \textbf{Social Infrastructure}: The presence of
  institutions, organizations, and services that support
  social well-being, such as community centers and support
  groups.
\end{enumerate}


